Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-05-19 write-up/fda-recurrent.tex
Update fda-recurrent.tex

>>>>

\section{Penalized mixed effects logistic model}

Here we derive a penalized adaptive Gaussian quadrature (PADQ) to fit the   penalized logistic mixed-effects model.  Here, for clarity, we write $Y_{ij} \ in \{ 0, 1 \}$ to be the sequence of binary indicators for participant $i = 1,\ldots,n$ and $j$ indexes the event and subsampled times.  We write $W_{ij}$ to denote the time-varying covariate.  Then the score equations for the penalized logistic regression with offset $\log(\pi_{ij})$ is written as
$$
\sum_{i=1}^n \sum_{j=1}^{k_i} \left( y_{ij} - \frac{1}{1+\exp (- W_{ij} \theta + \log (\pi_{ij}) )} \right) - \frac{1}{2 \sigma^2} \sum_{k=3}^{K_b} \beta_k^2 - \frac{1}{2 \sigma^2} (K_b - 3).
$$
We derive the iteratively re-weighted least squares algorithm next.

\subsection{Penalized adaptive Gaussian quadrature}

In standard logistic mixed-effects model, the likelihood is given by
$$
\sum_{i=1}^n \int \left( \frac{\exp(W_{ij} \theta + Z_{ij} b_i + \log \pi_{ij})}{1 + \exp(W_{ij} \beta + Z_{ij} b_i + \log \pi_{ij})} \right)^{y_{ij}} \left( \frac{1}{1 + \exp(W_{ij} \beta + Z_{ij} b_i + \log \pi_{ij})} \right)^{1-y_{ij}} \phi (b_i; \sigma_b^2) db_i
$$
